BPMN Analyzer 2.0: Instantaneous, Comprehensible, and Fixable Anomaly Detection for Realistic BPMN Models

### 2024-06-25 main.tex
Cleanup
Add overview
Add abstract

%%
%% One can fix some overfills
% \sloppy

@@

%%
%% Rights management information.
%% CC-BY is the default license.
\copyrightyear{2024}
\copyrightclause{Copyright for this paper by its authors.
  Use permitted under Creative Commons License Attribution 4.0
  International (CC BY 4.0).}

%%
%% This command is for the conference information
\conference{BPM 2024: Demos and Resources,
  September 01--06, 2024, Krakow, PL}

% TODO: Rename Rust BPMN Analyzer to BPMN Analyzer 2.0 on my website and maybe somewhere on GitHub.
\title{BPMN Analyzer 2.0: Instantaneous, Comprehensible, and Fixable Anomaly Detection for Realistic BPMN Models}

\author[1]{Tim Kräuter}
[email=tkra@hvl.no]
\author[1]{Patrick Stünkel}
[email=patrick.stuenkel@hvl.no]
\author[1]{Adrian Rutle}
[email=aru@hvl.no]
\author[1]{Yngve Lamo}
[email=yla@hvl.no]
\author[2,1]{Harald König}
[email=harald.koenig@fhdw.de]
\address[1]{Western Norway University of Applied Sciences, Bergen, Norway}
\address[2]{FHDW Hannover, Germany}

\begin{abstract}
  The tool is available online.
\end{abstract}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\begin{keywords}
BPM,
Verification,
Soundness,
Safeness
\end{keywords}

@@

% Details can be found here: https://bpm2024.agh.edu.pl/call-for-demos-and-resources/

@@

@@

\section{Maturity of the tool}
% Scalability tests (instantaneous)
Improves upon our previous BPMN Analyzer tool~\cite{krauterFormalizationAnalysisBPMN2023}.
% bpmn.io forum link/mention

@@

\section{Related work?}

@@

%%
%% If your work has an appendix, this is the place to put it.
% \appendix

@@

%%
%% End of file

>>>>

% One can fix some overfills
% \sloppy

@@

% Rights management information. CC-BY is the default license.
\copyrightyear{2024}
\copyrightclause{Copyright for this paper by its authors.
  Use permitted under Creative Commons License Attribution 4.0
  International (CC BY 4.0).}

\conference{BPM 2024: Demos and Resources, September 01-06, 2024, Krakow, PL}

\title{BPMN Analyzer 2.0: Instantaneous, Comprehensible, and Fixable Anomaly Detection for Realistic BPMN Models}

\author[1]{Tim Kräuter}
[email=tkra@hvl.no]
\author[1]{Patrick Stünkel}
[email=past@hvl.no] % patrick.stuenkel@hvl.no
\author[1]{Adrian Rutle}
[email=aru@hvl.no]
\author[1]{Yngve Lamo}
[email=yla@hvl.no]
\author[2,1]{Harald König}
[email=harald.koenig@fhdw.de]
\address[1]{Western Norway University of Applied Sciences, Bergen, Norway}
\address[2]{FHDW Hannover, Germany}

\begin{abstract}
Many business process models have control-flow anomalies, such as deadlocks or livelocks, which can hinder proper execution.
In this paper, we introduce our new tool that can instantaneously identify anomalies in BPMN models, make them comprehensible for modelers, and even suggest corrections to resolve them automatically.
We demonstrate that our tool's detection is instantaneous, i.e., it takes less than 500ms, by benchmarking our tool against synthetic BPMN models with increasing size and state space complexity, as well as realistic models provided in the literature.
Moreover, the tool directly displays detected anomalies in the model and provides an interactive visualization.
Additionally, it provides fixes to resolve the anomalies found, which are not currently available in other tools.
The tool is open-source, modular, extensible, and integrated into a popular BPMN modeling tool.
\end{abstract}

\begin{keywords}
BPM,
Verification,
Control-flow Analysis,
BPMN model checking,
Soundness,
Safeness
\end{keywords}

@@

% Details can be found here: https://bpm2024.agh.edu.pl/call-for-demos-and-resources/
% 5 pages including references
% Extended version on GitHub and then on Arxiv once submitted

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=\linewidth]{images/overview}
	\caption{Overview of the tool}
	\label{fig:overview}
\end{figure}

@@

\section{Maturity of the tool}
% Scalability tests (instantaneous)
Improves upon our previous BPMN Analyzer tool~\cite{krauterFormalizationAnalysisBPMN2023}.
% bpmn.io forum link/mention: https://forum.bpmn.io/t/automatic-bpmn-control-flow-analysis-and-resolution/11150

@@

\section{Related work?}
% Could cite my other extended version and put that on arxiv.

@@

% If your work has an appendix, this is the place to put it.
% \appendix

@@
